Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-16 doc/journal/fpgapaperfinal/FPGAPaper/partitioning.tex
Replaced oldfpaper with a citation
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4546 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

\section{Adding Partitioning to the CAD Flow}
\label{sec:CADflow}
TODO: Javeed

Given that the number of signals that can cross the interposer between FPGA dice is considerably more limited than within an FPGA, using a partitioner to divide the circuit into one partition per die is a promising CAD flow.

>>>>

\section{Adding Partitioning to the CAD Flow}
\label{sec:CADflow}
Given that the number of signals that can cross the interposer between FPGA dice is considerably more limited than within an FPGA, using a partitioner to divide the circuit into one partition per die is a promising CAD flow.
